Supervised Learning for Psychological Attention to High School Students

### 2020-11-18 article/inputs/svm.tex
[ article ] Added polynomial kernel svm explanation.

The Linear Kernel SVM had the worst performance in comparison to the others.
This fact can be seen in Table \ref{tab:linear_SVM}, in which is observed that
this machine does not classify any data point to the class 1 as the sensitivity
value is 0 for the three datasets.

@@

Lastly, it is also seen that in Figs.
\ref{fig:SVM-linear1a}-\ref{fig:SVM-linear1c},
\ref{fig:SVM-linear2a}-\ref{fig:SVM-linear2c} that the data are sparsed over
some discrete lines. This also verifies the realized projection as the variables
of this figures are discrete.

\begin{figure*}
    \centering
    \begin{subfigure}[b]{0.32\textwidth}
        \centering
        \includegraphics[width=\textwidth]{figs/svm-poly-contour-0-3.pdf}
        \caption{}
    \end{subfigure}
    \begin{subfigure}[b]{0.32\textwidth}
        \centering
        \includegraphics[width=\textwidth]{figs/svm-poly-contour-0-4.pdf}
        \caption{}
    \end{subfigure}
    \begin{subfigure}[b]{0.32\textwidth}
        \centering
        \includegraphics[width=\textwidth]{figs/svm-poly-contour-0-5.pdf}
        \caption{}
    \end{subfigure}

    \begin{subfigure}[b]{0.32\textwidth}
        \centering
        \includegraphics[width=\textwidth]{figs/svm-poly-contour-1-3.pdf}
        \caption{}
    \end{subfigure}
    \begin{subfigure}[b]{0.32\textwidth}
        \centering
        \includegraphics[width=\textwidth]{figs/svm-poly-contour-1-4.pdf}
        \caption{}
    \end{subfigure}
    \begin{subfigure}[b]{0.32\textwidth}
        \centering
        \includegraphics[width=\textwidth]{figs/svm-poly-contour-1-5.pdf}
        \caption{}
    \end{subfigure}

    \begin{subfigure}[b]{0.32\textwidth}
        \centering
        \includegraphics[width=\textwidth]{figs/svm-poly-contour-2-3.pdf}
        \caption{}
    \end{subfigure}
    \begin{subfigure}[b]{0.32\textwidth}
        \centering
        \includegraphics[width=\textwidth]{figs/svm-poly-contour-2-4.pdf}
        \caption{}
    \end{subfigure}
    \begin{subfigure}[b]{0.32\textwidth}
        \centering
        \includegraphics[width=\textwidth]{figs/svm-poly-contour-2-5.pdf}
        \caption{}
    \end{subfigure}
    \caption{Polynomial kernel SVM contour with real labels.}
    \label{fig:SVM-poly}
\end{figure*}

>>>>

The Linear Kernel SVM had the worst performance in comparison to the others
SVMs. This fact can be seen in Table \ref{tab:linear_SVM}, in which is observed
that this machine does not classify any data point to the class 1 as the
sensitivity value is 0 for the three datasets.

@@

Lastly, it is also seen that in Figs.
\ref{fig:SVM-linear1a}-\ref{fig:SVM-linear1c},
\ref{fig:SVM-linear2a}-\ref{fig:SVM-linear2c} that the data are sparsed over
some discrete lines. This also verifies the realized projection as the variables
of this figures where measured as discrete variables in the used survey.

The Polynomial Kernel SVM had the best performance in the SVM category,
reflected in Table \ref{tab:poly_SVM}. One important thing to notice is that the
machine, as well as the RBF kernel SVM, was able to learn the class 0 for all
the datasets. This fact shows that the dynamic of class 0 is easier to
generalize and, probably, is linearly separable from class 1.

On the other hand, as shown by Figs. \ref{fig:SVM-poly3a}-\ref{fig:SVM-poly3c},
it is seen that class 0 is detailed (mostly) by the points in the middle of the
graph. This underlies a problem in classifying these data points as they do not
present any drastic behavior. In this manner, this SVM was able to classify it
with some precision and shows that more data are required to fully train the
machine to learn class 1.

\begin{figure*}
  \centering
  \begin{subfigure}[b]{0.32\textwidth}
    \centering \includegraphics[width=\textwidth]{figs/svm-poly-contour-0-3.pdf}
    \caption{}
    \label{fig:SVM-poly1a}
  \end{subfigure}
  \begin{subfigure}[b]{0.32\textwidth}
    \centering \includegraphics[width=\textwidth]{figs/svm-poly-contour-0-4.pdf}
    \caption{}
  \end{subfigure}
  \begin{subfigure}[b]{0.32\textwidth}
    \centering \includegraphics[width=\textwidth]{figs/svm-poly-contour-0-5.pdf}
    \caption{}
    \label{fig:SVM-poly1c}
  \end{subfigure}

  \begin{subfigure}[b]{0.32\textwidth}
    \centering \includegraphics[width=\textwidth]{figs/svm-poly-contour-1-3.pdf}
    \caption{}
    \label{fig:SVM-poly2a}
  \end{subfigure}
  \begin{subfigure}[b]{0.32\textwidth}
    \centering \includegraphics[width=\textwidth]{figs/svm-poly-contour-1-4.pdf}
    \caption{}
  \end{subfigure}
  \begin{subfigure}[b]{0.32\textwidth}
    \centering \includegraphics[width=\textwidth]{figs/svm-poly-contour-1-5.pdf}
    \caption{}
    \label{fig:SVM-poly2c}
  \end{subfigure}

  \begin{subfigure}[b]{0.32\textwidth}
    \centering \includegraphics[width=\textwidth]{figs/svm-poly-contour-2-3.pdf}
    \caption{}
    \label{fig:SVM-poly3a}
  \end{subfigure}
  \begin{subfigure}[b]{0.32\textwidth}
    \centering \includegraphics[width=\textwidth]{figs/svm-poly-contour-2-4.pdf}
    \caption{}
  \end{subfigure}
  \begin{subfigure}[b]{0.32\textwidth}
    \centering \includegraphics[width=\textwidth]{figs/svm-poly-contour-2-5.pdf}
    \caption{}
    \label{fig:SVM-poly3c}
  \end{subfigure}
  \caption{Polynomial kernel SVM contour with real labels.}
  \label{fig:SVM-poly}
\end{figure*}

Lastly, it is seen that Figs. \ref{fig:SVM-poly1a}-\ref{fig:SVM-poly1c},
\ref{fig:SVM-poly2a}-\ref{fig:SVM-poly2c} are not critical in separating the
data. This occurs because the independent variable in these plots is discrete
and probably does not contain much information surrounding the problem. This
will be also be highlighted by the decision tree.
